```{r, echo=FALSE}
cat_loop_name <-  as.character(select(filter(cat_counts, row_number() == i), CategoryName))
data <- filter(nw_data, CategoryName == cat_loop_name)
```

# `r cat_loop_name`
cat
\begin{columns}[T]
    \begin{column}{0.30\textwidth} %first column
    Top Products
    \scriptsize
```{r}
#http://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf
arrange(data, desc(Quantity)) %>%
  head(n = 5) %>%
  select(Product = ProductName, Quantity) %>%
  arrange(desc(Quantity)) %>%
  kable(format = "latex", booktabs = TRUE) %>%
  #kable_styling(latex_options = "striped") %>% 
  #kable_styling(full_width = F) %>%
  column_spec(1, width = "0.9in")
```
    \normalsize
    \end{column}
    \hfill
  \begin{column}{0.30\textwidth} %second column
  Top Customers
      \scriptsize
```{r}
arrange(data, desc(Quantity)) %>%
  head(n = 5) %>%
  select(`Contact Name`= ContactName, Quantity) %>%
  arrange(desc(Quantity)) %>%
  kable(format = "latex", booktabs = TRUE) %>%
  #kable_styling(latex_options = "striped") %>% 
  #kable_styling(full_width = F) %>%
  column_spec(1, width = "0.9in")
```
      \normalsize
   \end{column}
   \hfill
     \begin{column}{0.30\textwidth} %third column
     Top Employees
       \scriptsize
```{r}
arrange(data, desc(Quantity)) %>%
  head(n = 5) %>%
  select(Employee = EmpName, Quantity) %>%
  arrange(desc(Quantity)) %>%
  kable(format = "latex", booktabs = TRUE) %>%
  #kable_styling(latex_options = "striped") %>% 
  #kable_styling(full_width = F) %>%
  column_spec(1, width = "0.9in")
```
       \normalsize
    \end{column}
\end{columns}

\vspace{2em}

\begin{columns}[T]
    \begin{column}{0.30\textwidth} %second row, first column heat map
    Monthly Sales
```{r, out.width="\\textwidth", fig.width=3.8,fig.height=1.8,fig.asp=NA}
g <- data %>%
  mutate(order_month = month(OrderDate),
         order_year = year(OrderDate)) %>%
  group_by(order_year, order_month) %>%
  summarize(monthly_sales = sum(Quantity * UnitPrice)) %>%
  my_calendarheatmap(
    df = .,
    xvar = "order_month",
    y = "order_year",
    fillvar = "monthly_sales",
    legendtitle = "Sales",
    fillvarformat = dollar
  )
g + theme(
  axis.text.y = element_text(size = rel(1)),
  axis.text.x = element_text(size = rel(0.8), face = "bold"),
  panel.background = element_rect(fill = "grey98"),
  plot.background = element_rect(fill = "grey98")
)
```
    \end{column}
    \hfill
    \begin{column}{0.30\textwidth} %second row, second column bar chart
    Top Products/Quantity
```{r, out.width="\\textwidth", fig.width=3.5,fig.height=1.8,fig.asp=NA}
g <- group_by(data, ProductName) %>%
  summarize(qty = sum(Quantity)) %>%
  arrange(desc(qty)) %>%
  head(n = 5) %>%
  ggplot(data = ., aes(x = reorder(ProductName, qty), y = qty)) +
  geom_bar(stat = "identity", fill = "#fc9272", width = 0.5) +
  coord_flip()

g + theme(
  axis.text.y = element_text(size = rel(1), hjust = 0),
  axis.text.x = element_text(size = rel(1), face = "bold"),
  panel.background = element_rect(fill = "grey98"),
  plot.background = element_rect(fill = "grey98"),
  axis.title = element_blank(),
  panel.border = element_blank(),
  panel.grid.major.x = element_line(color = "gray90")
)

```
    \end{column}
    \hfill
     \begin{column}{0.30\textwidth} %second row, third column bar chart
     Top Products/Sales
```{r, out.width="\\textwidth", fig.width=3.5,fig.height=1.8,fig.asp=NA}
g <- group_by(data, ProductName) %>%
  summarize(sales = sum(UnitPrice)) %>%
  arrange(desc(sales)) %>%
  head(n = 5) %>%
  ggplot(data = ., aes(x = reorder(ProductName, sales), y = sales)) +
  geom_bar(stat = "identity", fill = "#fc9272", width = 0.5) +
  scale_y_continuous(labels = dollar) +
  coord_flip()

g + theme(
  axis.text.y = element_text(size = rel(1), hjust = 0),
  axis.text.x = element_text(size = rel(1), face = "bold"),
  panel.background = element_rect(fill = "grey98"),
  plot.background = element_rect(fill = "grey98"),
  axis.title = element_blank(),
  panel.border = element_blank(),
  panel.grid.major.x = element_line(color = "gray90")
)

```
    \end{column}
\end{columns}





